---
title: "Parctical Machine Learning Assigment"
author: "Marco Antonio Béjar Villalba."
date: "1/27/2021"
output: md_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(caret)
library(randomForest)
```

# Context

One thing that people regularly do is quantify how  much of a particular activity they do, but they rarely quantify how well they do it. In this project, your goal will be to use data from accelerometers on the belt, forearm, arm, and dumbell of 6 participants.

Using devices such as Jawbone Up, Nike FuelBand, and Fitbit it is now possible to collect a large amount of data about personal activity relatively inexpensively. These type of devices are part of the quantified self movement – a group of enthusiasts who take measurements about themselves regularly to improve their health, to find patterns in their behavior, or because they are tech geeks. One thing that people regularly do is quantify how much of a particular activity they do, but they rarely quantify how well they do it. In this project, your goal will be to use data from accelerometers on the belt, forearm, arm, and dumbell of 6 participants. They were asked to perform barbell lifts correctly and incorrectly in 5 different ways. More information is available from the website here: http://web.archive.org/web/20161224072740/http:/groupware.les.inf.puc-rio.br/har (see the section on the Weight Lifting Exercise Dataset). [1]

# Analisis

I have loaded the data and analized it as follows:

```{r message=FALSE, warning=FALSE}
urlPMLTraining<-"https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv"
filePMLTraining<-"pml-training.csv"

urlPMLValidation<-"https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv"
filePMLValidation<-"pml-validation.csv"

if(!file.exists(filePMLTraining)){
  download.file(urlPMLTraining,filePMLTraining)
}

if(!file.exists(filePMLValidation)){
  download.file(urlPMLValidation,filePMLValidation)
}


dataTrainingAndTesting<-read.csv(filePMLTraining)
dataValidation<-read.csv(filePMLValidation)
```

So there is a data set for training and another that will be used to fill a test in coursera,
so in this paper the analysis is focused in the training data set which I split in order to get 
a training and a test data set.

```{r message=FALSE, warning=FALSE}
dataTrainingAndTesting$classe<-as.factor(dataTrainingAndTesting$classe)
dataTrainingAndTesting<-dataTrainingAndTesting[,c(160,grep(pattern = "_x$|_y$|_z$",x=names(dataTrainingAndTesting)))]

dataValidation<-dataValidation[,c(grep(pattern = "_x$|_y$|_z$",x=names(dataValidation)))]

set.seed(3304)

inTrain=createDataPartition(dataTrainingAndTesting$classe,p=0.7,list = FALSE)

dataTraining<-dataTrainingAndTesting[inTrain,]
dataTesting<-dataTrainingAndTesting[-inTrain,]
```

I transform the classe variable in a factor just for convenience and split the data set also I get out some variables, my
thesis is that (after have reviewed the data set) the meaningful variables are those that give information about the acceleration
of the movement, and these are those that finish with _x, _y, and _z, so the ones that describes acceleration on the three 
axis, I have run some exercises using all the variables and I have found that my thesis is in practice true or at least true 
enough to build a good model (besides it is the time factor because some models last a lot of time in training using all the
variables).

After that I construct the models, I will use GBM, Forest and Random Forest to compare them.

```{r message=FALSE, warning=FALSE, cache=TRUE}
modelForest<-train(classe~.,data = dataTraining,method="rpart")
#modelGBM<-train(classe~.,data = dataTraining,method="gbm")
#I got a freez using train, or it is so intensive that I though it was a freez so I used randomForest.
modelRandomForest<-randomForest(classe~.,data=dataTraining,type="class")

```





[1]
Velloso, E.; Bulling, A.; Gellersen, H.; Ugulino, W.; Fuks, H. Qualitative Activity Recognition of Weight Lifting Exercises. Proceedings of 4th International Conference in Cooperation with SIGCHI (Augmented Human '13) . Stuttgart, Germany: ACM SIGCHI, 2013.

Read more: http://groupware.les.inf.puc-rio.br/har#ixzz6kmFRRrJa
